\LARGE{Approximate Code: A Cost-Effective Erasure Code for MultimediavApplications in Cloud Storage Systems}\\

### 2019-03-25 paper.tex
version 0.3.1 code design but with errors

\begin{abstract}
Erasure codes are commonly used to ensure data availability in cloud storage systems, where video data produced by autopilot, multimedia industry and security monitoring occupies large amounts of space. 
Typical erasure codes, such as Reed-Solomon (RS) codes or XOR-based codes use several parity disks to fully recover failure disks. 
However, this is expensive, not only because the scenes in which multiple disks are simultaneously damaged are relatively rare, but also because they do not consider redundant information inside the data, which results in multiple complete parity disks being excessive.

@@

\subsection{Existing Erasure Codes}
RS/LRC/CLAY/SD/STAIR…
XOR-based
RS-based
RAID6
MSR

@@

\subsection{Our Motivation}
Based on Table 1, the existing erasure codes cannot meet the requirements of video applications in the cloud storage system due to the following reasons. First, existing erasure codes generally reach or exceed 3DFTS, and use more than 3 parity disks. However, the simultaneous damage of 3 disks is very rare, and the storage overhead paid for this is too large. Second, the existing erasure codes provide the same fault tolerance for all data without distinction, which results in the same reliability of important data that is sensitive to errors and data that is robust. To solve these two problems, we propose a new erasure code called approximation code. It provides different fault tolerance between important and non-critical data to reduce storage overhead and protect critical data better.

@@

In the $n$ chunks of each stripe, we use $m$ parity chunks, and there are $s \times t$ additional symbols in the remaining $n-m$ chunks for encoding. Our goal is to provide different reliability for important and general data, so we assume that normal data can tolerate damage of up to $m$ chunks, while important data can tolerate damage of up to $m+s$ chunks. Figure \ref{TEST-apcode-74222} shows an example of an approximate code for $n = 7$, $r = 4$, $m = 2$, $t=2$ and $s = 2$.
\begin{figure}[ht]
\centering
\includegraphics[width=0.4\textwidth]{photo/TEST-apcode-74222.JPG}
\caption{TEST--A sample of Approximate Code with n = 7, r = 4, m = 2, t=2 and s = 2.}
\label{TEST-apcode-74222}
\end{figure}

\subsection{Design of Approximate Code}
\subsection{Encoding and Decoding Processes}
\subsection{Proof of Correctness}
\subsection{Properties of Approximate Code}

>>>>

\begin{abstract}
Erasure codes are commonly used to ensure data availability in cloud storage systems, where video data produced by autopilot, multimedia industry and security monitoring occupies large amounts of space. 
Typical erasure codes, such as Reed-Solomon (RS) \cite{macwilliams1977theory} codes or XOR-based codes use several parity disks to fully recover failure disks. 
However, this is expensive, not only because the scenes in which multiple disks are simultaneously damaged are relatively rare, but also because they do not consider redundant information inside the data, which results in multiple complete parity disks being excessive.

@@

\subsection{Existing Erasure Codes}
RS/LRC/CLAY/SD/STAIR???

XOR-based

RS-based

RAID6

MSR

@@

\subsection{Our Motivation}
Based on Table [], the existing erasure codes cannot meet the requirements of video applications in the cloud storage system due to the following reasons. First, existing erasure codes generally reach or exceed 3DFTS, and use more than 3 parity disks. However, the simultaneous damage of 3 disks is very rare, and the storage overhead paid for this is too large. Second, the existing erasure codes provide the same fault tolerance for all data without distinction, which results in the same reliability of important data that is sensitive to errors and data that is robust. To solve these two problems, we propose a new erasure code called approximation code. It provides different fault tolerance between important and non-critical data to reduce storage overhead and protect critical data better.

@@

In the $n$ chunks of each stripe, we use $m$ parity chunks, and there are $s \times t$ additional symbols in the remaining $n-m$ chunks for encoding. Our goal is to provide different reliability for important and general data, so we assume that normal data can tolerate damage of up to $m$ chunks, while important data can tolerate damage of up to $m+s$ chunks. Figure \ref{TEST-apcode-75222} shows an example of an approximate code for $n = 7$, $r = 4$, $m = 2$, $t=2$ and $s = 2$.
\begin{figure}[ht]
\centering
\includegraphics[width=0.4\textwidth]{photo/TEST-apcode-75222.JPG}
\caption{TEST--A sample of Approximate Code with n = 7, r = 5, m = 2, t=2 and s = 2.}
\label{TEST-apcode-75222}
\end{figure}

\subsection{Design of Approximate Code}
We label $n$ disks from $D_0$ to $D_{n-1}$. Among them, $D_{n-m}$ to $D_{n-1}$ are parity disks. We label the data disks with $d_{i,j}$, the important data parity sectors with $x_{i,j}$ and the normal parity check sectors with $y_{i,j}$. The following equation represents the method to calculate $x_{i,j}$, $y_{i,j}(i<t)$ and $y_{i,j}(i \geqslant t)$

\begin{equation}
    x_{i,j} = \sum_{k=0}^{n-m-s-1} \alpha_k^{j+1} d_{i,k}
\end{equation}
\begin{equation}
    \mathop{y_{i,j}}\limits_{i<t} = \sum_{k=0}^{n-m-s-1} \alpha_k^{s+j+1} d_{i,k}
\end{equation}

\subsection{Encoding and Decoding Processes}
\subsection{Proof of Correctness}
\subsection{Properties of Approximate Code}
